DATA 621 - Business Analytics and Data Mining

### 2020-11-02 HW4/HW4_Draft.Rmd
Variable Table

#

>>>>

# DATA EXPLORATION
## Variables
The data is composed of the following variables:

|VARIABLE NAME|DEFINITION|THEORETICAL EFFECT|
|-|-|-|
|INDEX|Identification Variable (do not use)|None|
|TARGET_FLAG|Was Car in a crash? 1=YES 0=NO|None|
|TARGET_AMT|If car was in a crash, what was the cost|None|
|AGE|Age of Driver|Very young people tend to be risky. Maybe very old people also.|
|BLUEBOOK|Value of Vehicle|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_AGE|Vehicle Age|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_TYPE|Type of Car|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_USE|Vehicle Use|Commercial vehicles are driven more, so might increase probability of collision|
|CLM_FREQ|# Claims (Past 5 Years)|The more claims you filed in the past, the more you are likely to file in the future|
|EDUCATION|Max Education Level|Unknown effect, but in theory more educated people tend to drive more safely|
|HOMEKIDS|# Children at Home|Unknown effect|
|HOME_VAL|Home Value|In theory, home owners tend to drive more responsibly|
|INCOME|Income|In theory, rich people tend to get into fewer crashes|
|JOB|Job Category|In theory, white collar jobs tend to be safer|
|KIDSDRIV|# Driving Children|When teenagers drive your car, you are more likely to get into crashes|
|MSTATUS|Marital Status|In theory, married people drive more safely|
|MVR_PTS|Motor Vehicle Record Points|If you get lots of traffic tickets, you tend to get into more crashes|
|OLDCLAIM|Total Claims (Past 5 Years)|If your total payout over the past five years was high, this suggests future payouts will be high|
|PARENT1|Single Parent|Unknown effect|
|RED_CAR|A Red Car|Urban legend says that red cars (especially red sports cars) are more risky. Is that true?|
|REVOKED|License Revoked (Past 7 Years)|If your license was revoked in the past 7 years, you probably are a more risky driver.|
|SEX|Gender|Urban legend says that women have less crashes then men. Is that true?|
|TIF|Time in Force|People who have been customers for a long time are usually more safe.|
|TRAVTIME|Distance to Work|Long drives to work usually suggest greater risk|
|URBANICITY|Home/Work Area|Unknown|
|YOJ|Years on Job|People who stay at a job for a long time are usually more safe|
